### 2019-07-12 manuscript/results.tex
Figures and tables in the supplement fixed

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P ploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDP.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node of the D/P ploidy model} % XXX
%\label{suppfigure:DPnodipasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+ $\delta$ ploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+ $\delta$, ploidy model} % XXX
%\label{suppfigure:DPasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+A/B ploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P D/P+A/B ploidy model} % XXX
%\label{suppfigure:DPnodipABasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+$\delta$+A/B ploidy model.  The axis is offset in one location so that the two overlapping distributions can be seen.} % XXX
\label{suppfigure:DPAB}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPABdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+$\delta$+A/B ploidy model.} % XXX
%\label{suppfigure:DPABasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C breeding system model} % XXX
\label{suppfigure:IC}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIC.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C breeding system model} % XXX
%\label{suppfigure:ICasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSInoretposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C+A/B, breeding system model} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrICAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C+A/B breeding system model} % XXX
%\label{suppfigure:ICABasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP ploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCP.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP ploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPnodipasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+$\delta$, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$ ploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+A/B polyploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPnodipABasr}
%\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+$\delta$+A/B, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPdeltaAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$+A/B, polyploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPABasr}
%\end{suppfigure}

>>>>

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDP.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of theM1. D/P ploidy model} % XXX
\label{suppfigure:DPnodipasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M1. D/P model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDPAB.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M4. D/P+A/B asym model} % XXX
\label{suppfigure:DPnodipABasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M4. D/P+A/B asym model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIC.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M11.I/C model} % XXX
\label{suppfigure:ICasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M11. I/C model} % XXX
\label{suppfigure:IC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrICAB.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M14. I/C+A/B asym model} % XXX
\label{suppfigure:ICABasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSIasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M14. I/C+A/B asym model} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCP.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the  M16. ID/CD/CP model} % XXX
\label{suppfigure:IDCDCPnodipasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the  M16. ID/CD/CP model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCPAB.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the  M19. ID/CD/CP+A/B asym model} % XXX
\label{suppfigure:IDCDCPnodipABasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhissenodipasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M19. ID/CD/CP+A/B asym model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}
